Pillar 1 - Sequential Pattern Mining

### 2019-02-05 Pillar 1 - Sequential Pattern Mining.Rmd
new headers
updating cumulative transcript, adds columns "courses_not_taken", "courses_all"

```{r TODO}
# TODO: compute corrected confidence for AR
# TODO: compute lhs.support, for grade, not taken and  
```

@@

### Preceding courses
```{r}
d_cumulative_transcript <-  d_transactions        %>%
  select(sequenceID, item, eventID)  %>%
  arrange(sequenceID, eventID, item) %>%
  group_by(sequenceID, eventID)      %>%
  summarize_all(paste, collapse=" ") %>%
  arrange(sequenceID, eventID)       %>%
  mutate(
    Cumulative_transcript=lag(Reduce(paste, item, accumulate=T)),
    Cumulative_transcript= str_split(Cumulative_transcript," ")
                                     )
```

@@

my_apriori <- function(data, appearance){

@@

      # impose restriction on lhs and rhs
      appearance = appearance,

      control = list(
        verbose = FALSE
      )

@@

```{r}
compute_support <- function(AR, data_support, type_rule){

@@

  AR %>%

    # include lhs.support
    mutate(
      lhs_course = str_remove_all(lhs, pattern = "_fail|_low")
      ) %>%
    left_join(
      select(data_support, item, !!enquo(type_rule)),
      by = c("lhs_course" = "item")
      ) %>%
    mutate(
      lhs.support = round(!!type_rule_enquo, 5)
      )  %>%
    select(
      - !!type_rule_enquo
      ) %>%

    # include rhs.support
    mutate(
      rhs_course = str_remove_all(rhs, pattern = "_fail|_low")
      ) %>%
    left_join(
      select(data_support, item, !!type_rule_enquo),
      by = c("rhs_course" = "item")
      ) %>%
    mutate(
      rhs.support = round(!!type_rule_enquo, 5)
      ) %>%
    select(
      - !!type_rule_enquo
      ) %>%

    # order variable
    select(
      lhs, rhs, support, count, confidence, rhs.support, lift, lhs.support
    )

@@

```{r}
make_AR <- function(data, appearance = NULL,
                    data_support, type_rule){

  data %>%
    my_apriori(appearance = appearance) %>%
    clean_AR %>%
    compute_support(data_support = data_support, type_rule = !!enquo(type_rule))

@@

#
# AR taken
AR_taken <- transactions %>%
  make_AR(
    data_support = d_support_take, 
    type_rule = rate.take
    )

#
# AR fail
AR_PF <- transactions_PF %>%
  make_AR(
    appearance = list(

      # impose lhs and rhs to be fail
      both = d_transactions %>%
        filter(PF == "fail") %>%
        distinct(`item_PF`) %>%
        pull
    ),

    data_support = d_support,
    type_rule = rate.fail
  )

#
# AR low
AR_PF <- transactions_HL %>%
  make_AR(
    appearance = list(

      # impose lhs and rhs to be fail
      both = d_transactions %>%
        filter(HL == "low") %>%
        distinct(`item_HL`) %>%
        pull
    ),

    data_support = d_support,
    type_rule = rate.low
  )

# TODO

# AR_not_taken <- my_apriori(transactions_Taken)

# AR_expanded_Grade <- my_apriori(transactions_expanded_Grade)

>>>>

@@

### Preceding courses
```{r}
d_cumulative_transcript <-  d_transactions        %>%
  select(sequenceID, item, eventID)  %>%
  arrange(sequenceID, eventID, item) %>%
  group_by(sequenceID, eventID)      %>%
  summarize_all(paste, collapse=" ") %>%
  arrange(sequenceID, eventID)       %>%
  mutate(
    course_all  = paste(unique(d_transactions$item), collapse = " "),
    course_all  = str_split(course_all, pattern = " "),

    course_now  = str_split(item, pattern = " "),

    course_past     = Reduce(paste, item, accumulate=T),
    course_past     = lag(course_past),
    course_past     = str_split(course_past, pattern = " ")) %>%
  ungroup() %>%
    mutate(
    course_past_now = purrr::map2(.x = course_past,
                                      .y = course_now,
                                      .f = union),
    course_not = purrr::map2( .x = course_all,
                              .y = course_past_now,
                              .f = setdiff)
    ) %>%
  mutate(item = str_split(item, pattern = " "))
```

@@

my_apriori <- function(data, appearance = NULL){

@@

      # impose restriction on what could be on the lhs and rhs of the rule
      appearance = appearance

@@

```{r}
compute_support <- function(AR, type_rule){

@@

  AR %>%
    left_join(
      select(d_support, item, !!type_rule_enquo),
      by = c("rhs" = "item")
      ) %>%
    mutate(
      rhs.support = round(!!type_rule_enquo, 5)
      ) %>%
    select(
      - !!type_rule_enquo
      ) %>%
    left_join(
      select(d_support, item, !!type_rule_enquo),
      by = c("lhs" = "item")
      ) %>%
    mutate(
      lhs.support = round(!!type_rule_enquo, 5)
      ) %>%
    select(
      - !!type_rule_enquo
      ) %>%
    select(
      lhs, rhs, support, count, confidence, rhs.support, lift
    )

@@

```{r}
make_AR <- function(data, appearance, type_rule){

  data %>%
    my_apriori(appearance = appearance) %>%
    clean_AR() %>%
    compute_support(type_rule = type_rule)

@@

AR_take <- make_AR(transactions)

# Generating asocciation rules
AR_taken <- my_apriori(transactions) %>%
  left_join(
    select(d_support_take, item, rate.take),
    by = c("rhs" = "item")
    ) %>%
  mutate(
    rhs.support = round(rate.take, 5)
    ) %>%
  select(
    - rate.take
    ) %>%
  left_join(
    select(d_support_take, item, rate.take),
    by = c("lhs" = "item")
    ) %>%
  mutate(
    lhs.support = round(rate.take, 5)
    ) %>%
  select(
    - rate.take
    ) %>%
  select(lhs, rhs, support, count, confidence, rhs.support, lift)

# creating vector of fail course
course_id_fail <- d_transactions %>%
  filter(PF == "fail") %>%
  distinct(`item_PF`)

AR_PF <- my_apriori(transactions_PF,
                    appearance = list(both = course_id_fail$`item_PF`))

# creating vector of low score course
course_id_low <- d_transactions %>%
  filter(HL == "low") %>%
  distinct(`item_HL`)

AR_HL <- my_apriori(transactions_HL,
                    appearance = list(both = course_id_low$`item_HL`))

AR_Grade <- my_apriori(transactions_Grade)

AR_not_taken <- my_apriori(transactions_Taken)

AR_expanded_Grade <- my_apriori(transactions_expanded_Grade)
